### 2019-10-25 paper/results.tex
Addressed issues

The thorium feed mechanism adopts continuous feed flow of external thorium from the thorium stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}. The molar fraction of the heavy metal 
in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
Additionally, the initial fissile material fraction was increased for the five fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the Beginning Of Life (BOL). 
Figure~\ref{fig:keff1} illustrates the effective multiplication factor 
dynamics during reactor operation for the thorium feed mechanism. As shown in 
Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) 
decreases sharply during the first 25 \gls{EFPY} of reactor operation for the first 
four cases. $k_{eff}$ decreases as a result of depletion of the initial 
fissile materials and production of poisonous fission products \gls{FPs}. Thus, the 
reactor becomes subcritical relatively quickly for alternative startup 
compositions, for example, $\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
years in the reactor-grade Pu case. The amount of $^{233}$U generated in 
the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) is not enough to maintain the reactor criticality and 
counteract parasitic neutron absorption. Nevertheless, 
the continuous feed flow of thorium and $^{233}$U helps to operate the 
\gls{SD-TMSR} for a lifetime-long period of time (Figure~\ref{fig:keff1} (U-233 case)). 
Additionally, the molar fraction of the LEU and reactor-grade Pu in the initial fuel composition was increased
more, consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (LEU and reactor-grade Pu cases)). Nevertheless, $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.

@@

Table~\ref{tab:tcoe} summarizes temperature coefficients calculated for three 
different initial fissile loads at the startup and at the equilibrium. By 
propagating the $k_{eff}$ statistical error provided by SERPENT-2, 
uncertainty for each temperature coefficient was calculated using formula:
\begin{align}
\delta\alpha &= \abs{\frac{1}{T_{i+1} - T_i}} \sqrt{\frac{\delta 
		k_{eff}^2(T_{i+1})}{k_{eff}^4(T_{i+1})}  
	+ \frac{\delta k_{eff}^2(T_i)}{k_{eff}^4(T_i)}}
\intertext{where}
\delta k_{eff} &= \mbox{statistical error for $k_{eff}$ from SERPENT-2 
output.} 
\nonumber
\end{align}
Notably, other sources of uncertainty are neglected, such as cross-section 
measurement error and approximations inherent in the density dependence on 
temperature.

When the fuel salt temperature increases, the density of the salt decreases, 
but at the same time, the total volume of fuel salt in the 
core remains constant because it
is bounded by the vessel. When the graphite 
temperature increases, the density of
graphite decreases, creating additional 
space for the salt. The cross-section temperatures for the fuel and moderator 
were changed from 900 to 1000 K to determine the temperature coefficients. 
This work considered five different cases:
\begin{enumerate}
	\item Fuel salt temperature (Doppler Effect) rising from 900 to 1000 K 
	(first row  in Table~\ref{tab:tcoe}).
	\item Fuel salt density decreasing from 3.3 to 3.233 g/cm$^3$ 
	(density change caused by temperature increase from	900 to 1000 K).
	\item Total fuel salt temperature (Doppler+density) rising from 900 to 
	1000 K.	
	\item Graphite temperature (Doppler Effect) rising from 900 to 1000 K.
	\item Whole reactor temperature rising from 900 K to 1000 K.
\end{enumerate}

In the first case, the fuel temperature change only impacts cross-section 
temperature. In the second case, changes in the fuel temperature only impact 
density, and the third case takes into account both effects. The geometry for 
these three cases is unchanged because the fuel is a liquid. However, when 
the graphite blocks heat up, both the density and the geometry changing due 
to the thermal expansion of solid graphite. The graphite linear thermal 
expansion is not a dominating factor \cite{li_optimization_2018}, and herein 
we focus only on Doppler Effect for the moderator temperature coefficient.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [b!]
	\caption{Temperature coefficients of reactivity for 3 different initial 
		fuel salt compositions at startup and equilibrium. Confidence interval 
		$\pm\sigma$ for all coefficients is between $0.11$ and $0.16$ pcm/K).}
	\begin{tabularx}{\textwidth}{ p{0.27\textwidth} | X X  X X  X X } \hline
		\multirow{3}{*}{\shortstack{Reactivity coefficient \\ (pcm/K)}} 
		& 
		\multicolumn{6}{c}{Startup fissile material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil. & Initial & Equil. & Initial & 
		Equil. \\ \hline
		Fuel salt temperature&$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
		\\ 
		Fuel salt density&$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
		Total salt fuel&$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
		\hline
		Graphite temperature&$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
		\\	\hline
		Total core&$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
	\end{tabularx}
	\label{tab:tcoe}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The \gls{FTC} is negative for all considered fuel compositions due to thermal 
Doppler broadening of the resonance capture cross-sections in the thorium. For the 
$^{233}$U case, the \gls{FTC} decreases in magnitude by $-25\%$ due to neutron 
spectrum hardening during the reactor operation. For Pu reactor-grade and TRU 
cases, the \gls{FTC} becomes more negative at the equilibrium, by $+31\%$ and 
$+14\%$, respectively. Spectrum softening for these fueling cases positively 
affects the \gls{FTC} magnitude, and this effect seems to be proportional to 
the spectrum shift.

>>>>

The thorium feed mechanism adopts continuous feed flow of external thorium from the thorium stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}. The molar fraction of the heavy metal 
in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
Additionally, the initial fissile material fraction was increased for the five fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the Beginning Of Life (BOL). 
Figure~\ref{fig:keff1} illustrates the effective multiplication factor 
dynamics during reactor operation for the thorium feed mechanism. As shown in 
Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) 
decreases sharply during the first 25 \gls{EFPY} of reactor operation for the first 
four cases. $k_{eff}$ decreases as a result of depletion of the initial 
fissile materials and production of poisonous fission products (FPs). Thus, the 
reactor becomes subcritical relatively quickly for alternative startup 
compositions, for example, $\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
years in the reactor-grade Pu case. The amount of $^{233}$U generated in 
the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) is not enough to maintain the reactor criticality and 
counteract parasitic neutron absorption. Nevertheless, 
the continuous feed flow of thorium and $^{233}$U helps to operate the 
\gls{SD-TMSR} for a lifetime-long period of time (Figure~\ref{fig:keff1} (U-233 case)). 
Additionally, the molar fraction of the LEU and reactor-grade Pu in the initial fuel composition was increased
more, consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (LEU and reactor-grade Pu cases)). Nevertheless, $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.

@@

Table~\ref{tab:tcoe} summarizes temperature coefficients calculated for three 
different initial fissile loads at the startup and at the equilibrium. By 
propagating the $k_{eff}$ statistical error provided by SERPENT-2, 
uncertainty for each temperature coefficient was calculated using formula:
\begin{align}
\delta\alpha &= \abs{\frac{1}{T_{i+1} - T_i}} \sqrt{\frac{\delta 
		k_{eff}^2(T_{i+1})}{k_{eff}^4(T_{i+1})}  
	+ \frac{\delta k_{eff}^2(T_i)}{k_{eff}^4(T_i)}}
\intertext{where}
\delta k_{eff} &= \mbox{statistical error for $k_{eff}$ from SERPENT-2 
output.} 
\nonumber
\end{align}
Notably, other sources of uncertainty are neglected, such as cross section 
measurement error and approximations inherent in the density dependence on 
temperature.

When the fuel salt temperature increases, the density of the salt decreases, 
but at the same time, the total volume of fuel salt in the 
core remains constant because it
is bounded by the vessel. When the graphite 
temperature increases, the density of
graphite decreases, creating additional 
space for the salt. The cross section temperatures for the fuel and moderator 
were changed from 900 to 1000 K to determine the temperature coefficients. 
This work considered five different cases:
\begin{enumerate}
	\item Fuel salt temperature (Doppler Effect) rising from 900 to 1000 K 
	(first row  in Table~\ref{tab:tcoe}).
	\item Fuel salt density decreasing from 3.3 to 3.233 g/cm$^3$ 
	(density change caused by temperature increase from	900 to 1000 K).
	\item Total fuel salt temperature (Doppler+density) rising from 900 to 
	1000 K.	
	\item Graphite temperature (Doppler Effect) rising from 900 to 1000 K.
	\item Whole reactor temperature rising from 900 K to 1000 K.
\end{enumerate}

In the first case, the fuel temperature change only impacts cross section 
temperature. In the second case, changes in the fuel temperature only impact 
density, and the third case takes into account both effects. The geometry for 
these three cases is unchanged because the fuel is a liquid. However, when 
the graphite blocks heat up, both the density and the geometry changing due 
to the thermal expansion of solid graphite. The graphite linear thermal 
expansion is not a dominating factor \cite{li_optimization_2018}, and herein 
we focus only on Doppler Effect for the moderator temperature coefficient.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [b!]
	\caption{Temperature coefficients of reactivity for 3 different initial 
		fuel salt compositions at startup and equilibrium. Confidence interval 
		$\pm\sigma$ for all coefficients is between $0.11$ and $0.16$ pcm/K).}
	\begin{tabularx}{\textwidth}{ p{0.27\textwidth} | X X  X X  X X } \hline
		\multirow{3}{*}{\shortstack{Reactivity coefficient \\ (pcm/K)}} 
		& 
		\multicolumn{6}{c}{Startup fissile material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil. & Initial & Equil. & Initial & 
		Equil. \\ \hline
		Fuel salt temperature&$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
		\\ 
		Fuel salt density&$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
		Total salt fuel&$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
		\hline
		Graphite temperature&$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
		\\	\hline
		Total core&$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
	\end{tabularx}
	\label{tab:tcoe}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The \gls{FTC} is negative for all considered fuel compositions due to thermal 
Doppler broadening of the resonance capture cross sections in the thorium. For the 
$^{233}$U case, the \gls{FTC} decreases in magnitude by $-25\%$ due to neutron 
spectrum hardening during the reactor operation. For Pu reactor-grade and TRU 
cases, the \gls{FTC} becomes more negative at the equilibrium, by $+31\%$ and 
$+14\%$, respectively. Spectrum softening for these fueling cases positively 
affects the \gls{FTC} magnitude, and this effect seems to be proportional to 
the spectrum shift.
